R Packages to Aid in Handling Web Access Logs

### 2016-01-01 paper/paper.Rmd
made the images show up correctly

---
title: R Packages to Aid in Handling Web Access Logs
author:
  - name: Oliver Keyes
    affiliation: Wikimedia Foundation
    address:
    - 149 New Montgomery Street, 6th floor
    - San Francisco, CA, 94105, USA
    email:  ironholds@gmail.com
  - name: Bob Rudis
    affiliation: Rapid7
    address:
    - line 1
    - line 2
    email:  author2@work
  - name: Jay Jacobs
    affiliation: Magical Python Land
    address:
    - line 1
    - line 2
    email:  author3@work
abstract: >
  Web access logs contain information on HTTP(S) requests and form a key part of both industry and academic explorations
  of human behaviour on the internet - explorations commonly performed in R. In this paper we explain and demonstrate
  a series of packages designed to efficiently read in, parse
  and munge access log data, allowing researchers to handle it easily.
preamble: >
output: rticles::rjournal_article
---
## Introduction

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{reading_benchmarks}
    \caption{Results of microbenchmark run: read\char`_squid versus base-R equivalent code}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{decoding_benchmarks}
    \caption{Results of microbenchmark run: \code{url\_decode} versus base-R equivalent code}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{parsing_benchmarks}
    \caption{Results of microbenchmark run: \code{url\_parse} versus httr's equivalent code}
\end{figure}

>>>>

---
title: R Packages to Aid in Handling Web Access Logs
author:
  - name: Oliver Keyes
    affiliation: Wikimedia Foundation
    address:
    - 149 New Montgomery Street, 6th floor
    - San Francisco, CA, 94105, USA
    email:  ironholds@gmail.com
  - name: Bob Rudis
    affiliation: Rapid7
    address:
    - line 1
    - line 2
    email:  author2@work
  - name: Jay Jacobs
    affiliation: BitSight
    address:
    - Boston, MA
    email:  jay@beechplane.com
abstract: >
  Web access logs contain information on HTTP(S) requests and form a key part of both industry and academic explorations
  of human behaviour on the internet - explorations commonly performed in R. In this paper we explain and demonstrate
  a series of packages designed to efficiently read in, parse
  and munge access log data, allowing researchers to handle it easily.
preamble: >
output: rticles::rjournal_article
---
## Introduction

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=14cm,keepaspectratio]{reading_benchmarks-jay}
    \caption{Results of microbenchmark run: read\char`_squid versus base-R equivalent code}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=14cm,keepaspectratio]{decoding_benchmarks-jay}
    \caption{Results of microbenchmark run: \code{url\_decode} versus base-R equivalent code}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=14cm,keepaspectratio]{parsing_benchmarks-jay}
    \caption{Results of microbenchmark run: \code{url\_parse} versus httr's equivalent code}
\end{figure}

### 2016-01-01 paper/paper.tex
made the images show up correctly

\abstract{
Web access logs contain information on HTTP(S) requests and form a key
part of both industry and academic explorations of human behaviour on
the internet - explorations commonly performed in R. In this paper we
explain and demonstrate a series of packages designed to efficiently
read in, parse and munge access log data, allowing researchers to handle
it easily.
}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Aggregation}. Aggregating URLs together is useful to identify,
  for example, the relative usage and popularity of particular pages in
  your data - but it becomes tougher if encoding is inconsistent,
  because two URLs could hold the same value but \emph{look} very
  different.
\item
  \textbf{Value selection}. With text-based data, regular expressions
  are a common way of filtering or selecting entries that meet
  particular conditions, but things become fuzzy when you have to look
  not just for particular characters (a space, say) but also the encoded
  values (\%20).
\item
  \textbf{Exploratory data analysis} (EDA). EDA is a common initial step
  to investigate a data set, examining the variables and values it
  contains and whether they meet a researcher's expectations - but on a
  practical basis it becomes difficult when the values aren't
  human-readable.
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Whether the X-Forwarded-For field contains any values;
\item
  Extracting the earliest non-invalid IP address in that field's values
  if so, and the contents of the IP address field if not.
\end{enumerate}

@@

\address{
Oliver Keyes\\
Wikimedia Foundation\\
149 New Montgomery Street, 6th floor\\ San Francisco, CA, 94105, USA\\
}
\href{mailto:ironholds@gmail.com}{\nolinkurl{ironholds@gmail.com}}

\address{
Bob Rudis\\
Rapid7\\
line 1\\ line 2\\
}
\href{mailto:author2@work}{\nolinkurl{author2@work}}

\address{
Jay Jacobs\\
Magical Python Land\\
line 1\\ line 2\\
}
\href{mailto:author3@work}{\nolinkurl{author3@work}}

>>>>

\abstract{%
Web access logs contain information on HTTP(S) requests and form a key
part of both industry and academic explorations of human behaviour on
the internet - explorations commonly performed in R. In this paper we
explain and demonstrate a series of packages designed to efficiently
read in, parse and munge access log data, allowing researchers to handle
it easily.
}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Aggregation}. Aggregating URLs together is useful to identify,
  for example, the relative usage and popularity of particular pages in
  your data - but it becomes tougher if encoding is inconsistent,
  because two URLs could hold the same value but \emph{look} very
  different.
\item
  \textbf{Value selection}. With text-based data, regular expressions
  are a common way of filtering or selecting entries that meet
  particular conditions, but things become fuzzy when you have to look
  not just for particular characters (a space, say) but also the encoded
  values (\%20).
\item
  \textbf{Exploratory data analysis} (EDA). EDA is a common initial step
  to investigate a data set, examining the variables and values it
  contains and whether they meet a researcher's expectations - but on a
  practical basis it becomes difficult when the values aren't
  human-readable.
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Whether the X-Forwarded-For field contains any values;
\item
  Extracting the earliest non-invalid IP address in that field's values
  if so, and the contents of the IP address field if not.
\end{enumerate}

@@

\address{%
Oliver Keyes\\
Wikimedia Foundation\\
149 New Montgomery Street, 6th floor\\ San Francisco, CA, 94105, USA\\
}
\href{mailto:ironholds@gmail.com}{\nolinkurl{ironholds@gmail.com}}

\address{%
Bob Rudis\\
Rapid7\\
line 1\\ line 2\\
}
\href{mailto:author2@work}{\nolinkurl{author2@work}}

\address{%
Jay Jacobs\\
BitSight\\
line 1\\ line 2\\
}
\href{mailto:jjacobs@bitsighttech.com}{\nolinkurl{jjacobs@bitsighttech.com}}
